The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Added new RQ1 results sections. Included sections for Enhancive, Corrective and Reductive changes.

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study. Follow that, we will introduce the company and API examined in this study.

@@

@@

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors
 in-depth study on each of the laws (more exhaustive) (suggested by Imed during Friday review)

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work 
       look up implications for practitioners 
       recommendations for the case company (need to put this somewhere)

>>>>

\section{Background} \label{existing_literature}
This section will introduce the fields of API design and software evolution, and provide a review of studies that are directly related to our study.

@@

Adaptive

@@

3. Future work: Summarise what the next steps could be.
Obvious benefit for Axis is that the more features == more applications == higher value for their camera. If they have many applications being developed by partners (In part due to the fact they have added more features to the camera API) then the value of their hardware and software will increase. This is probably the case for many other APIs but would need to be studied in some detail to determine the truth behind the statement.
       -->Suggest a similar study which looks at business factors

Random tips n trickz:
       Look up the papers from the conference (especially regarding the discussion/conclusion)
       discussion = revisiting research questions (and maybe structuring around industry/academia)
       conclusion = summary part, main final points and future work
